---
title: "ProjectPart3_HalderSoumya"
author: "Soumya Halder"
date: "3/1/2020"
output:
  word_document: default
  html_document:
    df_print: paged
    keep_md: true
---

All the required packages are load at the beginning.

```{r include=FALSE, warning=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(MASS)
library(VGAM)
library(nnet)
```


* We create a multinomial variable *Y* using distance variable with the following definition:
Y = 1 if distance < 1000
Y = 2 if 1000 < = distance < 2500
Y = 3 otherwise
Now, we won't use the distance variable further and assume that the order for variable Y is unknown.

```{r}
faa_clean <- read.csv("D:/MS BANA/Spring 20/Stat Modelling 7042/Week 2/faa_clean.csv")
faa_clean$airplane_make <- as.factor(faa_clean$airplane_make)
faa_clean <- faa_clean %>%
                  mutate(Y = case_when(
                              distance < 1000 ~ 1,
                              distance >= 1000 & distance < 2500 ~ 2,
                              TRUE ~ 3
                  ))
head(faa_clean)
str(faa_clean)
faa_clean$Y <- as.factor(faa_clean$Y)
faa_clean$Y1 <- as.numeric(faa_clean$Y)
summary(faa_clean)
```


* A histogram is plotted to check the distribution of variable Y.Most occurences are of Y=2 followed by 1 and then 3.

```{r}
faa_clean %>% ggplot(aes(x = Y1)) +
                    geom_histogram(binwidth = 0.5) +
                    scale_x_continuous(breaks = seq(1, 3, 1)) +
                    xlab("Y")
```


* Data preparation: It is observed while removing all rows containing NA values, all occurences of *Y=1* also get removed. In our previous observations, we conculded that *speed_ground* and *speed_air* are highly correlated with the latter providing better results on the response variable. Since, the data gets highly affected here, we will use *speed_ground* to maintain better data quality.

```{r}
faa_clean_na_rm <- na.omit(faa_clean)
summary(faa_clean_na_rm)
```


* A new dataframe with only the predictor variables are created and then treated for the NA values present in duration column.

```{r}
faa_clean_na <- faa_clean[, c("duration", "no_pasg", "speed_ground", "height", "pitch", "airplane_make", "Y")]
faa_clean_na <- na.omit(faa_clean_na)
summary(faa_clean_na)
```

* Model builiding: We fit a multinomial model with Y as response and all other variables as predictors. The coefficients and their std errors can be noted in the below result. Here, *Y=1* has been used as a reference category. Hence, if *speed_ground* increases by 1 unit, the probability of Y=1 goes down by exp(0.244) i.e. 0.27% and a corresponding increasing in Y=2. 
```{r}
mmod <- multinom(Y ~ ., data = faa_clean_na)
summary(mmod)
```

* Let's fit a model using stepwise AIC method. We obtain only 4 predictor variables to be significant. Next, we'll calculate if these 2 models have high variances among them by performing a chi-squared test.
```{r}
mmod.aic <- step(mmod, trace = 0)
summary(mmod.aic)
```

* Difference between deviances of the 2 models
```{r}
deviance(mmod.aic) - deviance(mmod)
```

* Differnce between degrees of freedom
```{r}
mmod.aic$edf
mmod$edf
mmod$edf - mmod.aic$edf
```


* The chi-squared test doesn't allow us to reject the null hypothesis that both models are same. Since the AIC model is simpler with fewer predictors, we'll choose it for future predictions.

```{r}
pchisq(deviance(mmod.aic) - deviance(mmod), mmod$edf - mmod.aic$edf, lower = F)
```


* The below table shows the actual and predicted classes for all sets of predictor values. It can be seen, that very few data points are misclassified.

```{r}
xtabs(~faa_clean_na$Y + predict(mmod.aic))
```


* We'll visualize the results with all predictor variables strating with *speed_ground*
```{r}

faa_clean_pred <- faa_clean_na[, c("speed_ground", "height", "pitch", "airplane_make", "Y")]
faa_clean_pred$predclass <- predict(mmod.aic, newdata = faa_clean_pred, type = "class")

faa_clean_pred %>% 
  ggplot(aes(x = speed_ground, y = predclass)) +
  geom_point()
```

There is slight difference between the above and below graph which plots the predictor with actual Y values.
```{r}
faa_clean_pred %>% 
  ggplot(aes(x = speed_ground, y = Y)) +
  geom_point()
```


* The below 2 graphs with *height* and *pitch* doesn't give a clear indication of what could be the predicted Y value.

```{r}
faa_clean_pred %>% 
  ggplot(aes(x = height, y = predclass)) +
  geom_point()

faa_clean_pred %>% 
  ggplot(aes(x = pitch, y = predclass)) +
  geom_point()
```

* In conclusion, below are the coefficients of interest which reflects the change in response for any change in predictor variables
```{r echo=FALSE, include=FALSE}
summary(mmod.aic)$coefficients
```
* *speed_ground* seems to be the most important factor in classifying classes
* With *speed_ground* higher than 100, Y gets classified as 3 which can hint at possible risky landing for the aircraft
* This is further confirmed with the high coefficient values of *speed_ground* in comparison with other variables
